A hybrid approach for news recommender system using optimization methods

### 2021-02-25 paper/paper.tex
updated candidate generation

        \emph{item\_id} & \emph{date} & \emph{source\_id} \\\midrule

        1 & 2021-01-08 22:08:39 & 9  \\
        2 & 2021-01-09 10:28:58 & 5  \\
        3 & 2021-01-09 14:20:34 & 12 \\
        \vdots & \vdots & \vdots  \\\bottomrule

@@

Goal of candidate generation step is to remove generally irrelevant items so furher algorithms won't suffer from the amount of data.

@@

\subsubsection{Demographic filtering}

@@

    \begin{itemize}
        \item \textit{recommendation\_list}: list of recommendations that consists of pairs (\textit{item\_id}, \textit{score})
        \item \textit{content\_based\_filtering} \& \textit{collaborative\_filtering}: sources of recommendation
    \end{itemize}

>>>>

        \emph{item\_id} & \emph{date} & \emph{source\_id} & \emph{category}\\\midrule

        1 & 2021-01-08 22:08:39 & 9  & politics, conflicts\\
        2 & 2021-01-09 10:28:58 & 5  & IT, social media\\
        3 & 2021-01-09 14:20:34 & 12 & accident\\
        \vdots & \vdots & \vdots & \vdots \\\bottomrule

@@

Goal of candidate generation step is to remove generally irrelevant items so furher algorithms won't suffer from the amount of data. Both time-based filtering and content-based filtering have their own weight at start. As user more interacting with the system, content-based filtering increasing its weight.

Using recommenders described below, we attach score to each item and pick top $n$ (e.g. $50 000$) items.

@@

\subsubsection{Content-based filtering (categories)}

As was told before, content-based filtering have its own impact weight, which is small at start (we don't want to restrict user from content just because he made some random clicks), but it inscreases as user interacts with the system and we may make predictions about his categorial preferences.

@@

    \begin{itemize}
        \item \textit{recommendation\_list}: list of recommendations that consists of pairs (\textit{item\_id}, \textit{score})
        \item \textit{content\_based\_filtering \& collaborative\_filtering}: sources of recommendation
    \end{itemize}
